Network Configuration Synthesis with Abstract Topologies \vspace{1cm}

### 2017-05-29 paper/abstraction/paper.tex
remove printing from command line

%% packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{pifont}

@@

\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^{\dagger\ddagger}$\and Todd Millstein$^{\dagger\S}$\and Jitendra Padhye$^\ddagger$\and David Walker$^*$}
{Princeton University$^*$ \hspace{0.2in} Intentionet$^\dagger$ \hspace{0.2in}  Microsoft$^\ddagger$ \hspace{0.2in}  University of California Los Angeles$^\S$}
%{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}

@@

\textbf{Abstract---}
We develop \sysname, a system to synthesize provably-correct
BGP (border gateway protocol) configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that only incremental changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate on concrete topologies.

@@

\section{Propane/AT overview}
\label{sec:overview}

@@

\para{Abstract topology}
Abstract topologies in \sysname define structural and role-based invariants that compactly describe all concrete networks that can emerge as the network evolves. They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed the abstractions to be able to precisely capture real network topologies, while being amenable to fault-tolerance analysis in the abstract domain.

@@

\para{Routing policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference. \sysname borrows syntax from \Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.

@@

\para{Fault-tolerance policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss. Operators can specify different tolerance levels for different pairs of abstract nodes. For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be robust to 1 failure.

@@

\section{Fault-tolerance Analysis}
\label{sec:analysis}

@@

\subsection{Inference rules}

@@

\subsection{Inference algorithm}

@@

\subsection{Expressiveness and precision}
\begin{figure}[t!]
  \begin{center}
\small
      \begin{tabular}{| l | c| c | c | c | c | }
      \hline
       & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
       & & Some & All & Some & All \\
       & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

\para{Results}
The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies coupled with shortest-path routing. (Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for determining reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs. Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
%
For instance, for the fat tree topology~\cite{fattree}, it only finds 1 path between any ToR and any Spine when there should always be at least two. However, in this case the analysis computes the correct worst case connectivity between any source ToR and any other destination aggregation or ToR router. A similar pattern occurs with other tree-based topologies.
For both recursive topologies, the analysis can only accurately determine reachability.

@@

The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order. Like the data center, it blocks private destinations from neighbors, drops transit traffic between certain neighbors but not others, and aggregates internal prefixes at the border of the network.
%
We scale the backbone network from 10 to 240 routers. To abstract it, we split it into two parts: border routers that connect to external neighbors and an internal core. We use one abstract node for the border routers and one for the network core with mincut annotations both within the core and between the core and border roles. For neighbors, there is one abstract role per commercial category.

@@

\sysname's compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor. We experimentally confirmed that our implementation provides this guarantee. For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate. In each case, we found the guarantee to hold; for prefix changes, only the originator's configuration changed. In contrast, all router configurations were modified with \Propane because it heavily uses prefix lists which are sensitive to such changes. While \Propane may be made friendlier to network evolution (e.g., prefix lists are unnecessary at aggregation routers), its fundamental limitation will remain because it does not understand roles and the network's structure that \sysname leverages.

@@

\para{Network synthesis} Many recent systems focus on allowing operators to specify their policies at a high level of abstraction. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and generates dataplane rules~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

\para{Topology design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2-fattree,bcube,dcell,hyperx,butterfly}. We do not develop new designs but develop abstractions that can capture these designs (and their evolution).

@@

\para{Network verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,batfish,bagpipe,arc,era,coalgebraic}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

@@

\para{Acknowledgments}
We thank the many network engineers, especially George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies. 
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 and Cisco award 677002.

>>>>

%% packages
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{xcolor}
\usepackage{url}
\usepackage{times}
\usepackage{xspace}
\usepackage{listings}
\usepackage{code}
\usepackage{tikz}
\usetikzlibrary{arrows,automata,positioning}
\let\proof\relax
\let\endproof\relax
\usepackage{amsthm}
\usepackage[labelfont=bf]{caption}
\usepackage{subcaption}
\usepackage{balance}
\usepackage{textcomp}
\usepackage{enumitem}
\usepackage{pifont}

\setlength{\bibsep}{1.8pt}

@@

\authorinfo{Ryan Beckett$^*$\and Ratul Mahajan$^{\dagger\ddagger}$\and Todd Millstein$^{\dagger\S}$\and Jitendra Padhye$^\ddagger$\and David Walker$^*$}
{Princeton University, USA$^*$ \hspace{0.2in} Intentionet, USA$^\dagger$ \hspace{0.2in}  Microsoft, USA$^\ddagger$ \hspace{0.2in}  UCLA, USA$^\S$}
%{\{rbeckett,dpw\}@cs.princeton.edu, \{ratul,padhye\}@microsoft.com, todd@cs.ucla.edu}

@@

\begin{abstract}
We develop \sysname, a system to synthesize provably-correct
BGP (border gateway protocol) configurations for large, evolving networks from high-level
specifications of topology, routing policy, and fault-tolerance
requirements. \sysname is based on new abstractions for capturing
parameterized network topologies and their evolution, and algorithms
to analyze the impact of topology and routing policy on fault
tolerance. Our algorithms operate entirely on abstract topologies.  We
prove that the properties established by our analyses hold for every
concrete instantiation of the given abstract topology. \sysname
also guarantees that only incremental changes to existing device configurations
are required when the network evolves to add or remove devices and
links. Our experiments with real-world topologies and policies show
that our abstractions and algorithms are effective, and that, for large
networks, \sysname synthesizes configurations two orders of magnitude
faster than systems that operate on concrete topologies.
\end{abstract}

@@

\section{Propane/AT Overview}
\label{sec:overview}

@@

\para{Abstract Topology}
Abstract topologies in \sysname define structural and role-based invariants that compactly describe all concrete networks that can emerge as the network evolves. They are encoded in the form of a graph homomorphism annotated with logical constraints about node and edge multiplicities.
%
We designed the abstractions to be able to precisely capture real network topologies, while being amenable to fault-tolerance analysis in the abstract domain.

@@

\para{Routing Policy} Routing policies in \sysname consist of an ordered sequence of $i)$ a predicate that matches a class of traffic; and $ii)$ paths that the traffic should take through the network, ranked per their relative preference. \sysname borrows syntax from \Propane~\cite{propane}, but instead of concrete predicates and paths, uses abstract predicates and paths.

@@

\para{Fault-Tolerance Policy} This policy specifies how many link failures the network should be able to withstand before traffic experiences connectivity loss. Operators can specify different tolerance levels for different pairs of abstract nodes. For instance, they may say that ToR to spine connectivity should be robust to 2 failures, \IE, no ToR-spine pair should lose connectivity as long as the number of simultaneous link failures is 2 or fewer; and ToR-to-ToR connectivity should be robust to 1 failure.

@@

\section{Fault-Tolerance Analysis}
\label{sec:analysis}

@@

\subsection{Inference Rules}

@@

\subsection{Inference Algorithm}

@@

\subsection{Expressiveness and Precision}
\begin{figure}[t!]
  \begin{center}
\small
      \begin{tabular}{| l | c| c | c | c | c | }
      \hline
       & \textbf{Fixed} & \multicolumn{2}{|c|}{\textbf{Reachability}} & \multicolumn{2}{|c|}{\textbf{K-paths}} \\ \hline
       & & Some & All & Some & All \\
       & & Pairs & Pairs & Pairs & Pairs \\ \hline

@@

\para{Results}
The bottom part of Figure~\ref{fig:analysis-precision} shows the results for all types of topologies with shortest-path routing. (Valley-free routing is not meaningful for non-tree-based topologies.) For all tree-based topologies, the analysis is precise for reachability, but for three of them, it does not compute a tight bound for disjoint paths for all router pairs. Specifically, it underestimates ToR-to-spine paths; it fails to account for some circuitous paths that traverse another spine because it could not disambiguate two concrete spines that map to the same abstract role.
%
For instance, for the fat tree topology~\cite{fattree}, it only finds 1 path between any ToR and any Spine when there should always be at least two. However, in this case the analysis computes the correct worst case connectivity between any source ToR and any other destination aggregation or ToR router. A similar pattern occurs with other tree-based topologies.
%
For both recursive topologies, the analysis can only accurately determine reachability.

@@

The backbone policy classifies neighbors into several categories based on commercial relationship~\cite{gao-rexford} and prefers paths through them in order. Like the data center, it blocks private destinations from neighbors, drops transit traffic between certain pairs of neighbors, and aggregates internal prefixes at the network border.
%
We scale the backbone network from 10 to 240 routers. We split it into two parts: border routers that connect to external neighbors and an internal core. We use one abstract node for the border routers and one for the network core with mincut annotations both within the core and between the core and border roles. For neighbors, there is one abstract role per commercial category.

@@

\sysname's compilation strategy guarantees that network evolution requires configuration changes only for nodes that acquire or lose a neighbor. We experimentally confirmed that our implementation provides this guarantee. For the networks we studied above, we made a range of changes, including adding and removing routers and pods and changing prefixes that routers originate. In each case, we found the guarantee to hold. In contrast, all router configurations were modified with \Propane because it heavily uses prefix lists which are sensitive to such changes. While \Propane may be made friendlier to network evolution,
%(e.g., prefix lists are unnecessary at aggregation routers), 
its fundamental limitation will remain because it does not understand roles and the network's structure that \sysname leverages.

@@

\para{Network Synthesis} Many recent systems allow operators to specify their policies at a high level of abstraction. These can be classified into two classes. The first class targets networks based on SDN (software-defined networking) and generates dataplane rules~\cite{foster:merlin,fattire,netgen}. The second class, to which our work belongs, targets conventional networks and generates control-plane router configurations~\cite{synet-synthesis,narain+:configassure,propane}.
%, based on which the routers interact and compute forwarding rules~\cite{propane,narain:lisa05,narain+:configassure}.
%Almost all large networks (old or new) use the conventional paradigm because that scales better~\cite{bgp-in-dc}.

@@

\para{Topology Design} Network topology design, especially for data centers, is another active research area, with researchers exploring designs with different properties~\cite{fattree,facebook-fattree,f10-fattree,vl2-fattree,bcube,dcell,hyperx,butterfly}. We do not develop new designs but develop abstractions that can capture these designs (and their evolution).

@@

\para{Network Verification}
A complementary approach to reducing configuration errors is to analyze the forwarding rules or the configuration of a network to ensure the absence of (a class of) bugs~\cite{anteater,hsa,veriflow,feamster+:rcc,batfish,bagpipe,arc,era,coalgebraic}. Our focus, in contrast, is on a correct-by-construction approach. It has the downside that operators must express policies in a new language, but it saves them from the challenging and time-consuming task of manual configuration generation.

@@

\acks
We thank George Chen and Lihua Yuan, who pointed out the importance of working with abstract topologies.
We also thank the PLDI reviewers, and especially our shepherd Alexandra Silva for comments on the paper. This work is supported in part by the National Science Foundation award CNS-1161595 and Cisco award 677002.
